\section{PSF Characterization}
In this section we give a brief overview of the PSF fitting procedure used by \texttt{PiFF}, our definitions of PSF related quantities and the fitting configuration used for the data.
\subsection{Fitting}
For a given single-visit image processed by the DRP, the PSF is fit independently on each CCD. 
Under the default DRP configuration, which does not include chromatic corrections, the PSF 
modeling is performed using \texttt{PiFF}. The input to \texttt{PiFF} is a catalog of all 
detected objects in the image, together with their positions in sky coordinates. From this 
catalog, \texttt{PiFF} selects two subsets of stars: a primary sample used to fit the PSF 
model and a smaller, reserved sample used for PSF diagnostic tests. A model is then fit to the stellar images to obtain a maximum-likelihood 
estimate of the PSF parameters (position, and optionally, wavelength) at each stellar location. Finally, the fitted model parameters are interpolated across 
the stellar sample to estimate the PSF over the full focal plane using a second order polynomial. To incorporate colour 
dependence in the PSF modeling, we provide \texttt{PiFF} with stellar colours derived using the 
Forward Global Calibration Method \citep[FGCM;][]{burke2017}, which are computed in a preceding 
step of the DRP.

\subsection{PSF Shape Definitions}
Equation \ref{eq:psf_residuals} shows the definitions for PSF size ($T$) and ellipticity ($e_1$ \& $e_2$) that are used in this work.
\begin{equation}
\label{eq:psf_residuals}
    \begin{aligned}
        T \equiv i_{xx} + i_{yy}  \\
        e_1 \equiv \frac{i_{xx}-i_{yy}}{i_{xx}+i_{yy}}\\
        e_2 \equiv \frac{2i_{xy}}{i_{xx}+i_{yy}}
    \end{aligned}
\end{equation}

For each quantity above ($T$, $e_1$, $e_2$), we also define the residual to be the difference between the measured value and the fit value of the model: $\delta X \equiv X_{\rm PSF} - X_{\rm model}$ and $\delta X/X \equiv (X_{\rm PSF}-X_{\rm model})/X_{\rm PSF}$.

\subsection{PSF Fitting Configuration}
We test several \texttt{PiFF} chromatic fitting configurations to minimize the error in the PSF model due to chromatic effects. 
We saw most improvement in the PSF fit by using a 2nd-order polynomial fit in spatial position and colour, with no significant improvement from using higher orders. 
The final configuration is shown below.
\lstinputlisting[language=Python]{finalizeCharacterizationConfig.py}